Twists of supersymmetric gauge theories

### 2019-08-28 paper.tex
4d n=1

@@

Let $R$ be a complex representation of $\mf g$.

The matter sector of the theory is labeled by the BRST fields:
\begin{itemize}
\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
\end{itemize} 
which together define the (abelian) local Lie algebra
\[
\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
\]
\subsection{Dimension 3}

>>>>

\brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}

@@

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
In addition, $4$-dimensional supersymmetry supports a chiral (anti-chiral matter) multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric Yang-Mills numerous times. 
The kinetic action for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ denotes the obvious pairing between $R$ and $R^*$. 
Super Yang-Mills couples to the matter via the action 
\[
S_{\rm couple} = \int \d^4 x \;
\]

The action by supersymmetry for the $4$-dimensional matter theory is encoded by a linear and quadratic functional
\begin{align*}
I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R
\end{align*}

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from hereon. 
Such supercharges are minimal (i.e. have 2d image).  
They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think}.  
The R-symmetry group is $U(1)$, and so the twisted theory by such a supercharge is always $\ZZ$-graded.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the $\SU(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto c \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda & \mapsto \chi + \psi_{1,0} + B_{0,2} \in \Omega^0(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg)
\end{align*}

The matter fields decompose as
\begin{align*}
\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
\psi_- & \mapsto \beta_0 + \beta_{2,0} \in \Omega^{0,0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) .
\end{align*}

%
%The matter sector of the theory is labeled by the BRST fields:
%\begin{itemize}
%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
%\end{itemize} 
%which together define the (abelian) local Lie algebra
%\[
%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
%\]
%\subsection{Dimension 3}
